\section{Scenario and Requirements}
\label{sec:scenario}
In this section, first the usual scenario of the system is described in detail. Then, the specific requirements related to system development are specified.

By registering in the platform, the translators start to declare their profiles. Regarding to each language pair, the price and duration per word is set. In the next step, the translators upload their previous translated documents. The documents are processed and used in text matching as well as  translation memory systems. As the last step, the translators fill the time table using the schedule system. They specify the time slots in which they are ready to work and potentially can be hired by clients.

The client starts searching for translators by uploading a document. Based on four criteria, the system searches and retrieves the three most relevant translators. These criteria are cost, delivery time, frequent cooperation and text matching. Related to each criterion, a weight is defined which specifies the importance of the criterion from the client's point of view.

Using the profiles of the translators as well client's document, the value for each criteria is estimated. Cost is calculated based on price per word and the number of words in the document. Delivery time is estimated using the schedule of the translator, duration per word and the number of words in the document. Finally, a text matching value is computed by processing the text and aggregating the similarity values between the query document and the previous translated documents of all the translators for the desired language pair.

After having calculated the values of different criteria, the system ranks the translators and represents the three most relevant ones to the client. The client chooses one and follows the payment process. By purchasing the order, the platform informs the translator and asks for confirmation. During translation, the client and translator are in contact using a chat system. After finishing the translation, a qualified proof-reader chosen by the client revises the text and may send some corrections to the translator. At the end, the proof-reader assesses the quality of the translation from different points of view (grammar, style, accuracy, content and language) by giving a score (1-5) of each of them.

The requirements considered in the project are as follows:
\begin{itemize}
	\item Wizard-like page for purchasing the order in a SPA (Single Page Application) structure.
	\item Indexing previous-translated texts and finding a function for aggregating their similarity values regarding to query document.
	\item Developing a ranking function in order to find the best three translators among all.
	\item Calculating delivery time based on translator's schedule.
	\item Web-Page as well as Web-API interface.
	\item Supporting payment process for different payment cards and methods.
	\item Short response time.
	\item Considering different languages and timezones.
\end{itemize}