\newcommand{\figurescaling}{0.7}
\input{config}
\input{title}

\begin{document}

\maketitle
\begin{abstract}
The report explains the details of design and developing process of a translator retrieval platform. The platform's objective is to suggest an appropriate translator to a client. It manages the process of translation until the last step. Additionally, by providing a translation memory system translators can exploit their previous translated texts in their new ones. C\texttt{\#}.NET and MS SQL SERVER are used as main platform and Lucene.NET is the text processor. The system is designed based on Data Driven Design (DDD) model. Windows Azure is the deployment environment.
\end{abstract}

\vfill
\tableofcontents
\newpage

\input{introduction}
\newpage
\input{problem}
\newpage
\input{architecture}
\newpage
\input{design}
\newpage
\input{development}
\newpage

\section{Conclusion}
\label{sec:conclusion}
In this report, we explain different aspects of implementing a translator retrieval system. We report designed architecture, applied tool as well as problems and pitfalls during development.

The project bring us deep understanding on development of an expert retrieval system in a web-based platform. During the system implementation, we confront many problems in the area of text processing, searching and information retrieval. Additionally, we try to apply the best practice on system design and develop regarding to software engineering point of view.
\newpage

\listoffigures
\bibliographystyle{plain}
\bibliography{report}

\end{document}
