In this section, first the framework's elements is denoted. Then the techniques for calculating documents similarity and some restrictions are described. At the end, the strategy for ranking and choosing the best possible translator is discussed.

\subsection{Framework Denotation}
As it is depicted in the following formula ,the profile of each translator related to the query (
$\overrightarrow{T_{i,q}}$) is a vector where $i$ is the iterator for translators and $q$ is the corresponding query. In the formula, $t_q$ and $c_q$ stand for estimated time and cost for translation. $e_q$ denotes the experience or knowledge of translator which is calculated based on similarity between query document and all previous-translated documents. The technique applied for calculating $e_q$ is explained further. $s$ shows the quality of translator and how previous tasks have been estimated. It is achieved by calculating the average value of correctors' feedbacks. The value is between one (very bad) to five (perfect).

\begin{center}
$\overrightarrow{T_{i,q}} = \{ t_{i,q}, c_{i,q}, e_{i,q}, s_i \}$ \\
\end{center}

After finishing the task and gathering feedbacks of clients, based on the offered values for each translation, feedback vectors can be built up. In the following formula $j$ denotes the iteration for feedbacks and $f_j$ stands for feedback value.

\begin{center}
$\overrightarrow{F_j} = \{ t_j, c_j, e_j, s_j, f_j \}$ \\
\end{center}

\subsection{Documents Similarity}
In order to calculate $e_q$, we need to figure out the similarity between query document and all previous-translated documents. The similarity is calculated by Lucene library and is denoted as $SIM$ function. Every pre-translated document is assessed by corrector's feedback ($f'$). In additional to these documents, every translator may submit some other documents which had been translated before and clearly not assessed. In the framework, we assume their quality as medium (two). In the following formula $d_iterator$ and $d_q$ stand for pre-translated and query documents. $n$ and $m$ are the number of pre-translated document inside and outside the framework.

\begin{center}
$e_{i,q} = \sum_{0<k<n} f'_k SIM(d_k, d_q) + \sum_{0<l<m} 2 SIM(d_l, d_q) $ \\
\end{center}

***TODO: The Lucene's similarity value does not have a special range and is a number greater than or equal to zero. Here there can be some discussions about the meaning of the achieved value or probable alternative solutions ***

\subsection{Ranking}
***TODO: Ranking method goes here***